---
title: "Generative Art"
author: "Dylan Li"
format: 
  html:
    theme: 
      light: flatly
    page-layout: article
    code-fold: true
    self-contained: true
    code-tools: true
    toc: true
execute:
  echo: true
  error: true
  message: false
  warning: false
embed-resources: true
editor: visual
---

## Libraries

```{r}
library(ggplot2)
library(tibble)
library(dplyr)
library(RColorBrewer)
```

## First Piece

### Color Selection

```{r}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}
```

### Ephemeral Wings

```{r}
pal <- sample_canva(seed = 104)

quakes |>
  ggplot(aes(x = long, y = lat, colour = depth, size = mag)) + 
  geom_point(show.legend = FALSE) + 
  theme_void() +
  scale_colour_gradientn(colours = pal)
```

A pair of wings made by numerous dots of varying sizes, almost void of color.

The seed determines the color palette for the image, and the color is determined by the depth of the earthquake.

## Second Piece

### Data Generation

```{r}
sample_data <- function(seed = NULL, n = 100, z = 1){
  if(!is.null(seed)) set.seed(seed)
  dat <- tibble(
    x0 = seq(0, -0.00000001 + z, by = 1/(n/z)),
    y0 = seq(z + 0, 0.00000001, by = -1/(n/z)),
    x1 = x0 + runif(n, min = -.2, max = .2),
    y1 = y0 + runif(n, min = -.2, max = .2),
    shade = runif(n), 
    size = runif(n)/n,
    shape = factor(sample(0:22, size = n, replace = TRUE))
  )
}
```

### Plotting

```{r}
polar_styled_plot <- function(data = NULL, palette) {
  ggplot(
    data = data,
    mapping = aes(
      x = x0,
      y = y0,
      xend = x1,
      yend = y1,
      colour = shade,
      size = size
    )) + 
    coord_polar(clip = "off") +
    scale_y_continuous(
      expand = c(0, 0),
      limits = c(0, 1), 
      oob = scales::oob_keep
    ) +
    scale_x_continuous(
      expand = c(0, 0), 
      limits = c(0, 1), 
      oob = scales::oob_keep
    ) + 
    scale_colour_gradientn(colours = palette) + 
    scale_size(range = c(0, 10)) + 
    theme_void() + 
    guides(
      colour = guide_none(),
      size = guide_none(),
      fill = guide_none(),
      shape = guide_none()
    )
}
```

## Shrimp

```{r}
dat <- sample_data(n = 5000, seed = 1, z = 1) 
pal <- sample_canva(seed = 17)

polar_styled_plot(data = dat, palette = pal) + geom_segment()

```

A lone, shrimp like spiral made of uncountably many bars.


The data generation generates a vector in sequential order at a set interval. The width of the interval is determined by the z parameter, the larger it is, the more times the art will spiral. A choice of 5000 bars were used to make the visual more appealing, as a lesser amount of bars makes it less compact and less interesting.